Turbulence in compact to giant HII regions

### 2022-07-08 strucfunc_paper.tex
Add a paragraph about the noise to sec 4.4

>>>>

For most of our sources \(B\noise / \sigma^2\los < 0.03 \) and the noise
has almost no effect on the structure function,
apart from at the very smallest separations,
resulting in a negligible influence on the other model parameters.
The exceptions are the Galactic regions Lagoon, Carina,
and especially the Extended Orion Nebula,
for which the noise is sufficiently large that the observed
structure function slope is significantly shallower than
the inferred slope \(m\) of the true model.
These sources also show the largest fluctuations of the
observed \(B(r)\) around the smooth fit
at intermediate scales
(see in particular Figure~\ref{fig:strucfunc-fit-Galactic}d),
which is probably due to the relatively small number of spectra.
